An Algorithm to Prune Integer Overflow Tests

### 2012-08-29 doc/Manuscript/CGO/paper.tex
Removed two directories.

\noindent
\paragraph{Dynamic Detection of Integer Overflows: }
Brumley \em{et al.}~\cite{Brumley07} have developed a tool, RICH, to detect
integer integer overflows.
Their approach consists in instrumenting every integer operation that might cause
to an overflow, underflow, or data loss.
Different from our method, RICH uses specific features of the x86 architecture
to reduce the instrumentation overhead.
Moreover, no static analysis is used to avoid unnecessary assertions, although
this improvement is cited as future work.

>>>>

\noindent
\paragraph{Dynamic Detection of Integer Overflows: }
Brumley {\em et al.}~\cite{Brumley07} have developed a tool, RICH, to detect
integer integer overflows.
Their approach consists in instrumenting every integer operation that might cause
to an overflow, underflow, or data loss.
Different from our method, RICH uses specific features of the x86 architecture
to reduce the instrumentation overhead.
Moreover, no static analysis is used to avoid unnecessary assertions, although
this improvement is cited as future work.
